Typed Functional Genetic Programming

### 2013-05-06 tex/thesis.tex
some preparations in v3
[tex] ...

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage{amsthm}

@@

% Stačí todle odkomentovat a dát nahoře LaTeX , pak DVI->PDF  a pak View PDF
%\includegraphics[scale=0.5]{logo.eps}

@@

@@

\chapter{Introduction}

@@

We will demonstrate $\lambda$-term generation on example. 
Again on $(\lambda f . (\lambda x . (f x) ))$. 
We would like to generate $\lambda$-term of a type 
$(\sigma \rightarrow \tau) \rightarrow (\sigma \rightarrow \tau)$
with $\Gamma = \{\}$.
\begin{align*}
	& ((\sigma \rightarrow \tau) \rightarrow (\sigma \rightarrow \tau),\{\}) \\ 
	\longmapsto & \bigg( \mbox{ {\Large $\lambda$ f . }}
	  ( \sigma \rightarrow \tau , \{ (f,\sigma \rightarrow \tau) \} ) 
	\quad \bigg)
	\\
	\longmapsto & 
	\bigg( \mbox{ {\Large $\lambda$ f . }}
		\bigg( \mbox{ {\Large $\lambda$ x . }}
	  	 	( \tau , \{ (f,\sigma \rightarrow \tau) , (x,\sigma) \} ) 
		\quad \bigg)  	 
	\quad \bigg)
	\\
	\longmapsto & 
	\bigg( \mbox{ {\Large $\lambda$ f . }}
		\bigg( \mbox{ {\Large $\lambda$ x . }}	  	 	
	  	 	\bigg( 
	  	 	  ( \sigma \rightarrow \tau , \{ (f,\sigma \rightarrow \tau) , (x,\sigma) \} ) 
			  \mbox{ \Vtextvisiblespace[1em] } 
			  ( \sigma , \{ (f,\sigma \rightarrow \tau) , (x,\sigma) \} ) \bigg) 
		\quad \bigg)  	 
	\quad \bigg)
	\\
	\longmapsto & 
	\bigg( \mbox{ {\Large $\lambda$ f . }}
		\bigg( \mbox{ {\Large $\lambda$ x . }}	  	 	
	  	 	\bigg( 
	  	 	  \mbox{ {\Large f}} 
			  \mbox{ \Vtextvisiblespace[1em] } 
			  ( \sigma , \{ (f,\sigma \rightarrow \tau) , (x,\sigma) \} ) \bigg) 
		\quad \bigg)  	 
	\quad \bigg)		
	\\
	\longmapsto & 
	\bigg( \mbox{ {\Large $\lambda$ f . }}
		\bigg( \mbox{ {\Large $\lambda$ x . }}	  	 	
	  	 	\bigg( 
	  	 	  \mbox{ {\Large f}} 
			  \mbox{ \Vtextvisiblespace[1em] } 
			  \mbox{{\Large x}} \bigg) 
		\quad \bigg)  	 
	\quad \bigg)
\end{align*}

\subsection{"Barendregt-like" inference and grammar rules}

@@

	\section{Inhabitation tree}
		\subsection{Inhabitation Machine}
	\section{Roadmap}
	\section{Conversion to SKI combinators}

@@

\chapter{ Designed system }	
	\section{Top level view}
	\section{Term generating}
		\subsection{A* algorithm}
	\section{Crossover}
		\subsection{Finding same types}
		\subsection{Two basic options}
		Resolve problems with free variables or avoid variables completely.

@@

\chapter{Conclusion}

>>>>

\usepackage[utf8]{inputenc}

\usepackage{qtree}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}

\usepackage{graphicx}

\usepackage{hyperref}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Stačí todle odkomentovat a dát nahoře LaTeX (F2) , pak DVI->PDF (F9)  a pak View PDF
%\includegraphics[scale=0.5]{logo.eps}
\includegraphics[scale=0.15]{logomff.png}

@@

%%% Následuje vevázaný list -- kopie podepsaného "Zadání diplomové práce".
%%% Toto zadání NENÍ součástí elektronické verze práce, nescanovat.

%%% Na tomto místě mohou být napsána případná poděkování (vedoucímu práce,
%%% konzultantovi, tomu, kdo zapůjčil software, literaturu apod.)

%% on tam měl %% \openright

\noindent
Dedication.

%%% Strana s čestným prohlášením k diplomové práci

\vglue 0pt plus 1fill

\noindent
I declare that I carried out this master thesis independently, and only with the cited
sources, literature and other professional sources.

\medskip\noindent
I understand that my work relates to the rights and obligations under the Act No.
121/2000 Coll., the Copyright Act, as amended, in particular the fact that the Charles
University in Prague has the right to conclude a license agreement on the use of this
work as a school work pursuant to Section 60 paragraph 1 of the Copyright Act.

\vspace{10mm}

\hbox{\hbox to 0.5\hsize{%
In ........ date ............
\hss}\hbox to 0.5\hsize{%
signature of the author
\hss}}

\vspace{20mm}
\newpage

%%% Povinná informační strana diplomové práce

\vbox to 0.5\vsize{
\setlength\parindent{0mm}
\setlength\parskip{5mm}

Název práce:
Název práce
% přesně dle zadání

Autor:
Jméno a příjmení autora

Katedra:  % Případně Ústav:
Název katedry či ústavu, kde byla práce oficiálně zadána
% dle Organizační struktury MFF UK

Vedoucí diplomové práce:
Jméno a příjmení s tituly, pracoviště
% dle Organizační struktury MFF UK, případně plný název pracoviště mimo MFF UK

Abstrakt:
% abstrakt v rozsahu 80-200 slov; nejedná se však o opis zadání diplomové práce

Klíčová slova:
% 3 až 5 klíčových slov

\vss}\nobreak\vbox to 0.49\vsize{
\setlength\parindent{0mm}
\setlength\parskip{5mm}

Title:
% přesný překlad názvu práce v angličtině

Author:
Jméno a příjmení autora

Department:
Název katedry či ústavu, kde byla práce oficiálně zadána
% dle Organizační struktury MFF UK v angličtině

Supervisor:
Jméno a příjmení s tituly, pracoviště
% dle Organizační struktury MFF UK, případně plný název pracoviště
% mimo MFF UK v angličtině

Abstract:
% abstrakt v rozsahu 80-200 slov v angličtině; nejedná se však o překlad
% zadání diplomové práce

Keywords:
% 3 až 5 klíčových slov v angličtině

\vss}

@@

%\chapter{Introduction}
\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction}

@@

We will demonstrate $\lambda$-term generation on example. 
Again on $(\lambda f . (\lambda x . (f x) ))$. 
We would like to generate $\lambda$-term of a type 
$(\sigma \rightarrow \tau) \rightarrow (\sigma \rightarrow \tau)$
with $\Gamma = \{\}$.
\begin{align*}
	& ((\sigma \rightarrow \tau) \rightarrow (\sigma \rightarrow \tau),\{\}) \\ 
	\longmapsto & \Big( \mbox{ {\Large $\lambda$f.}}
	  ( \sigma \rightarrow \tau , \{ (f,\sigma \rightarrow \tau) \} ) 
	~ \Big)
	\\
	\longmapsto & 
	\Big( \mbox{ {\Large $\lambda$f. }}
		\Big( \mbox{ {\Large $\lambda$x. }}
	  	 	( \tau , \{ (f,\sigma \rightarrow \tau) , (x,\sigma) \} ) 
		~ \Big)  	 
	~ \Big)
	\\
	\longmapsto & 
	\Big( \mbox{ {\Large $\lambda$f. }}
		\Big( \mbox{ {\Large $\lambda$x. }}	  	 	
	  	 	\Big( 
	  	 	  ( \sigma \rightarrow \tau , \{ (f,\sigma \rightarrow \tau) , (x,\sigma) \} ) 
			  \mbox{ \Vtextvisiblespace[1em] } 
			  ( \sigma , \{ (f,\sigma \rightarrow \tau) , (x,\sigma) \} )  \Big) 
		~ \Big)  	 
	 ~ \Big)
	\\
	\longmapsto & 
	\Big( \mbox{ {\Large $\lambda$f. }}
		\Big( \mbox{ {\Large $\lambda$x. }}	  	 	
	  	 	\Big( 
	  	 	  \mbox{ {\Large f}} 
			  \mbox{ \Vtextvisiblespace[1em] } 
			  ( \sigma , \{ (f,\sigma \rightarrow \tau) , (x,\sigma) \} ) \Big) 
		~ \Big)  	 
	~ \Big)		
	\\
	\longmapsto & 
	\Big( \mbox{ {\Large $\lambda$f. }}
		\Big( \mbox{ {\Large $\lambda$x. }}	  	 	
	  	 	\Big( 
	  	 	  \mbox{ {\Large f}} 
			  \mbox{ \Vtextvisiblespace[1em] } 
			  \mbox{{\Large x}} \Big) 
		~ \Big)  	 
	~ \Big)
\end{align*}

\subsection{"Barendregt-like" inference and grammar rules}
\label{barlike}

@@

\section{Inhabitation tree}

Now we will introduce \textit{Inhabitation tree}, structure slightly different from
\textit{Inhabitation machine}, which was introduced in \cite{barendregt10} by Henk Barendregt.
We can think about Inhabitation tree as about unfolded Inhabitation machine.
\\\\
\textbf{TODO}: TALK ABOUT And-Or-graph \\
\textbf{TODO}: TALK ABOUT "Barendregt-like" subsection \ref{barlike}
\\\\
Let's see some example:

\begin{align*}
\sigma =& ~ \mathbb{B} \rightarrow  \mathbb{B} \rightarrow  \mathbb{B} \\ 
\Gamma =& \{ ~ true : \mathbb{B}  \\
        &  , ~ nand :  \mathbb{B} \rightarrow \mathbb{B} \rightarrow \mathbb{B} ~ \}
\end{align*}

\Tree
[.\text{ $\mathbb{B} \rightarrow \mathbb{B} \rightarrow \mathbb{B}$ }  
	[.\textbf{$\lambda$x_1 x_2 } 
		[.\text{ $\mathbb{B}$ } 
			\textbf{true}  
			[.\textbf{nand} 
				\qroof{ ~~ $\dotsb$ ~~ }.\text{ $\mathbb{B}$ }
				\qroof{ ~~ $\dotsb$ ~~ }.\text{ $\mathbb{B}$ } 
			]
			\textbf{x_1}
			\textbf{x_2}
		]
	]
]

		\subsection{Inhabitation Machine}
	\section{Roadmap}
	\section{Conversion to SKI combinators}

@@

\chapter{ Designed system }	
	\section{Top level view}
		\subsection{Comments about main source files}
			\subsubsection{ Eva.hs }
	\section{Term generating}
		\subsection{A* algorithm}
	\section{Crossover}
		\subsection{Finding same types}
		\subsection{Two basic options}
		Resolve problems with free variables or avoid variables completely.

@@

%\chapter{Conclusion}
\chapter*{Conclusion}
\addcontentsline{toc}{chapter}{Conclusion}

\begin{thebibliography}{9}

\bibitem{barendregt10}
  Henk Barendregt, Wil Dekkers, Richard Statman,
  \emph{Lambda Calculus With Types}.
  Cambridge University Press,
  2010. \\
  \url{http://www.cs.ru.nl/~henk/book.pdf}

\end{thebibliography}
